\chapter*{General conclusion}
\addcontentsline{toc}{chapter}{General conclusion}
\markboth{General conclusion}{}
This report summarizes three months of work, commitment and learning at the VatoSmart agency as part of an end-of-studies internship with the intention of obtaining a bachlor's degree in computer science. 
During these three months, our mission was to participate effectively in the implementation of an information system developed around the Odoo ERP in its version 12, for our client.\\
In order to start our project, the first challenge was to understand the general context of the project. We had to capture a maximum of dissatisfaction aspects that are the subject of the problem and criticism of the existing presented in the first chapter of this report.\\
The structure of this report reflects the logic of the SCRUM work methodology that we used to properly plan the development process of our project.\\
First of all, we approached the notion of ERPs to clarify some notions that proved to be very important to the understanding of the project. We then devoted a two weeks  to the analysis phase before starting the first Sprint, which is the subject of the design, development and implementation of a configuration module  dedicated to the platform administrator. We then continued with two other sprints dedicated to the other two increments of our project, namely the employee managment module and the travel order managment module. 
By the way, we find this work has been instructive in that we have had the opportunity to learn about new technologies and acquire new personal and professional skills. We draw a positive balance of the realization of this project including both a theoretical aspect on the concept of ERPs and the benefits of their implementation and practical on the modular architecture of ERP Odoo .\\
And like any application, this project remains an evolutionary prototype, and remains open to any possible perspective. \\
It is proposed to extend this project with other modules to cover a maximum of activities for the client.
