
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Design and Implementation of a marketplace module}

\author{Mohammed Amine El Amri}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{the National Diploma of Science and Technology}
\speciality{Computer Science}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerName{Ms. Amira Hasnaoui}
\proFramerSpeciality{--}

%% Encadrant académique
\academicFramerName{Ms. Hayet Mogaadi}
\academicFramerSpeciality{--}

%% Entreprise d'accueil
\companyName{VatoSmart}

%% Année universitaire
\collegeYear{2019 - 2020}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{I authorize the student to submit his internship report for review.}

\academicSignSentence{I authorize the student to submit his internship report for review.}

%%% AR
\arabicAbstract{تم إنجاز هذا العمل داخل شركة \textLR{VatoSmart} في إطار مشروع ختم الدروس و ذلك للحصول على الشهادة الوطنية الأساسية في العلوم و التكنولوجيا وهو يتألف من إنشاء ثلاث وحدات تم تطويرها حول \textLR{Odoo ERP} ، من أجل إدارة بعض المهام الإدارية والموظفين وعملية سفر الأعمال. }


\arabicAbstractKeywords{\textLR{Python, ERP, Odoo, XML}}

%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{Ce projet a été réalisé au sein de l'agence VatoSmart dans le cadre d'un stage de fin d'études effectué à l'Institut supérieur d'informatique (ISI) en vue de l'obtention du diplôme national de science et de technologie.
Il consiste à mettre en place trois modules développés autour de l'ERP Odoo, afin de gérer certaines tâches administratives, les employés et le processus de voyage d'affaires.}

\frenchAbstractKeywords{Python, ERP, Odoo, XML}

%%% EN
\englishAbstract{This project was carried out within the VatoSmart agency as part of an internship for final studies carried out at Higher Institution of Computer Science (ISI) in order to obtain the National Diploma of Science and Technology.
It consists of setting up three modules  developed around the Odoo ERP, in order to manage some administrative tasks, the employees and business travel process.}

\englishAbstractKeywords{Python, ERP, Odoo, XML}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{true}

\companyEmail{contact@vatosmart.tn}
\companyTel{55 217 949}
\companyFax{71 222 222}
\companyAddressAR{مركب I1 الطابق الثاني - مكتب 224 - المركب التكنولوجي بالغزالة - أريانة}
\companyAddressFR{BLOC I1 2ème étage - Bureau 224 - El Gazala Technopark - Ariana}